---
title: "Optimization using GA"
output: html_document
---

## Derive parameters

- Read data

```{r}
library(readr)
library(dplyr)
library(lubridate)

# Passenger drop on, off data
passen_final<-read_csv("data/passen_final.csv")

# DTG data of taxis
dtg_final<-read_csv("data/dtg_final_saved.csv")

# Median travel time between zones
TravelTime<-read_csv("data/TravelTime.csv")

# All passenger pick-up/drop-off in 3 months
### For derive standard deviation of demand
passen_all<-read_csv("data/passen_all.csv")

# Road length by grid (unit: kilometer)
road_length <- read.csv("data/road_length_by_grid.csv")
road_length<- road_length %>% filter(grid_id %in% ROI) %>% select(grid_id,LengthSum) %>% arrange(grid_id)

# Speed over zones by time
speed_by_zone <- read.csv("data/speed_by_zone_time.csv")
```

- Parameters

```{r}
# Time index; 30 minutes intervals
Time<-ymd_hms("2017-03-02 00:00:00")+hours(0:23)
Time<-c(Time,Time + minutes(30)) %>% sort()

# Length of grid (1km)
L<-1

# Road density by zones
Rho<-road_length$LengthSum # Road density by grids

N<-42 # Number of grids
M<-5
Phi <-vector("list",48) # Call demand density of zones #Phi
Xi <-vector("list",48) # Street demand density of zones #Xi 
k<-0.1 # Ratio between Street and Call demand
Psi<-vector("list",48) # Arrival rate of zones 

Eta<-vector("list",48) # Maximum discharge rate at hubs 

A <- vector("list",48) # Density of vacant vehicles at zones
B <- vector("list",48) # Density of vacant vehicles at stations
v <- vector("list",48) # Vehicle speed
Epsilon <- vector("list",48) # Travel time between zones
```


## Data preprocessing for calculating passengers' demand
- 승하차 자료를 이용하여 수요를 추출
- 3월 2일 오전 12시부터 오후 11시 45분까지 60분 간격으로 총 48개
- Grid의 갯수는 총 42개

```{r}
# 42 Grids
ROI<-sort(c(61, 105, 136, 146, 154, 168, 184, 189, 190, 191, 194, 196, 199, 206, 225, 229, 230, 231, 233, 240, 241,
       245, 246, 251, 253, 257, 258, 260, 266, 268, 318, 320, 375, 391, 395, 400, 424, 442, 459, 464, 465, 468))

ROI_hub <- c(91, 92, 94, 95, 99)

# Make 30 minutes interval
passen_final$dprt_time_30min <- floor_date(passen_final$dprt_time,"30 minutes")
passen_final$arrvl_time_30min <- floor_date(passen_final$arrvl_time,"30 minutes")
```

- Street-hailing rate(Xi) and Calling rate(Phi)

```{r}
# 42개의 그리드에서 발생한 통행만 추출 > 각 그리드별/시간대별 수요 도출 
tmp<-passen_final %>% filter(trv_dist>0,dprt_grid %in% ROI, dprt_st_id ==0) %>% group_by(dprt_grid,dprt_time_30min) %>% summarise(n=n())
tmp2<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
tmp2 <-tmp2 %>% left_join(tmp, by=c("grid_id"="dprt_grid","time"="dprt_time_30min"))
tmp2[is.na(tmp2$n),]$n<-0

# Call과 Street를 구분
tmp2$Phi<-tmp2$n*k
tmp2$Xi<-tmp2$n*(1-k)
tmp2<-tmp2 %>% arrange(time,grid_id)

# Save Phi and Xi to list
for(i in 1:48) {
 Phi[[i]]<-tmp2$Phi[(N*i-N+1):(N*i)] 
} 

for(i in 1:48) {
 Xi[[i]]<-tmp2$Xi[(N*i-N+1):(N*i)] 
} 
```


- Arrival rate at zones (Psi)

```{r}
tmp <- passen_final %>% filter(trv_dist>0, arrvl_grid %in% ROI) %>% group_by(arrvl_grid,arrvl_time_30min) %>% do(n=length(unique(.$carnum)))
tmp$n<-unlist(tmp$n)
tmp <- passen_final %>% filter(trv_dist>0, arrvl_grid %in% ROI) %>% group_by(arrvl_grid,arrvl_time_30min) %>% summarise(n=n())
arate<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
arate <-arate %>% left_join(tmp, by=c("grid_id"="arrvl_grid","time"="arrvl_time_30min"))
arate[is.na(arate$n),]$n<-0
arate<-arate %>% arrange(time,grid_id)

for(i in 1:48) {
 Psi[[i]]<-arate$n[(N*i-N+1):(N*i)] 
} 
```

- Maximum discharge rate at hubs (Eta)

```{r}
# Station 
tmp<-passen_final %>% filter(trv_dist>0,dprt_grid %in% ROI, dprt_st_id !=0) %>% group_by(dprt_st_id,dprt_time_30min) %>% summarise(n=n())
drate<-data.frame(dprt_st_id=rep(sort(unique(tmp$dprt_st_id)),each=48),time=Time)
drate <-drate %>% left_join(tmp, by=c("dprt_st_id"="dprt_st_id","time"="dprt_time_30min"))
drate[is.na(drate$n),]$n<-0
drate<-drate %>% arrange(time,grid_id)

for(i in 1:48) {
 Eta[[i]]<-drate$n[(M*i-M+1):(M*i)] 
}
```

## DTG raw data를 이용한 빈택시 댓수 가공 (A, B)
- dtg_final2 를 이용함
- 3월 2일 오전 12시부터 오후 12시 00분까지 30분 간격으로 총 48개
- 매 시간마다의 빈차 댓수 매핑
- Grid의 갯수는 총 42개
- Vacant taxis in zones (A)

```{r}
# Make time variable every 30 minutes
dtg_final$dprt_time_30min <- floor_date(dtg_final$time2,"30 minutes")

# Find the number of empty taxis in each grid every hour
tmp<-dtg_final %>% 
  filter(time2 %in% Time, # Filter DTG-raw only in every hour 
         onoff==0 # Extract only vacant taxi 
         )%>% 
  group_by(dprt_grid, dprt_time_30min) %>% # Grid 번호, 시각으로 그룹
  summarise(A=n()) # 각 그룹별 택시 댓수 추출

# 빈 시간대, 0값으로 채우기 
tmp2<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
tmp2 <-tmp2 %>% left_join(tmp, by=c("grid_id"="dprt_grid","time"="dprt_time_30min"))
tmp2[is.na(tmp2$A),]$A<-0
tmp2<-tmp2 %>% arrange(time,grid_id)

# A를 list로 저장
for(i in 1:48) {
 A[[i]]<-tmp2$A[(N*i-N+1):(N*i)]
} 
```

- Vacant taxis in hubs (B)

```{r}
# Find the number of empty taxis in each grid every hour
tmp<-dtg_final %>% 
  filter(time2 %in% Time, # Filter DTG-raw only in every hour 
         onoff==0 # Extract only vacant taxi 
         ) %>% 
  group_by(st_id, dprt_time_30min) %>% # Grid 번호, 시각으로 그룹
  summarise(B=n()) # 각 그룹별 택시 댓수 추출

# 빈 시간대, 0값으로 채우기 
tmp2<-data.frame(st_id=rep(ROI_hub,each=48),time=Time)
tmp2 <-tmp2 %>% left_join(tmp, by=c("st_id"="st_id","time"="dprt_time_30min"))
tmp2[is.na(tmp2$B),]$B<-0
tmp2<-tmp2 %>% arrange(time,st_id)

# A를 list로 저장
for(i in 1:48) {
 B[[i]]<-tmp2$B[(M*i-M+1):(M*i)] 
} 
```


## Travel time 도출 (E) - 미완성

- 각 grid에 차량이 존재하지 않을 경우, 가장 가까운 지역의 차량이 호출된다고 가정
- 이를 표현하기 위해서는 그리드간의 통행시간 정보가 필요함
- TravelTIme object는 2017년 1월부터 3월까지의 승하차 자료를 기반으로 grid 간 통행 시간의 median 값을 도출한 테이블임
- 생각해보니 이건 최적화 할 때 쓸 일이 없음

```{r}
# 빈 시간대, 0값으로 채우기 
for(i in 1:48) {
 epsilon[[i]]<-TravelTime %>% filter(dprt_time_30min == Time[i]) 
} 
```

## Speed over zones by time
```{r}
speed_by_zone$time_30min <- ymd_hms(as.character(speed_by_zone$time_30min))

# 빈 시간대, 0값으로 채우기 
tmp2<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
tmp2 <-tmp2 %>% left_join(speed_by_zone %>% select(-X,-n), by=c("grid_id"="dprt_grid","time"="time_30min"))
tmp2[is.na(tmp2$mean_speed),]$mean_speed<-mean(speed_by_zone$mean_speed)
tmp2<-tmp2 %>% arrange(time,grid_id)
tmp2$mean_speed[239]<-tmp2$mean_speed[239]+20

# A를 list로 저장
for(i in 1:48) {
 v[[i]]<-tmp2$mean_speed[(N*i-N+1):(N*i)] 
} 

```

## Derive standard deviation of demand
- Approximate with the root square of demand value
- Assuming the demand follows Poisson distribution

```{r}
SD_Xi <- lapply(Xi,sqrt)
SD_Phi <- lapply(Phi,sqrt)
SD_Psi <- lapply(Psi,sqrt)
SD_Eta <- lapply(Eta,sqrt)
```


# Optimization using GA

## Desicion variable

```{r}
X <- 0
Y <- 0
i<-2
T_1 <- 0
T_2 <- 0
```

## Constraint

- Cons 1
X : Relative number of relocation taxis of all zones
Y : Relative number of relocation taxis of all hubs
K : Additional vehicles to have to be put

```{r}
X + Y + K == 0
```

- Cons 2
```{r}
A_delta <- lapply(1:48, function (i) A[[i]] + (-Xi[[i]]-Phi[[i]]+Psi[[i]]) + X) # Equation (3) 
```

- Cons 3 
```{r}
B_delta <- lapply(1:48, function (i) B[[i]] - Eta[[i]] - 0.65 * SD_Eta[[i]] + Y) 
```

- Cons 4
```{r}
A_delta[[i]] - 0.65*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]])

for (i in 1:48){
  print(sum(A_delta[[i]] - 0.65*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]])))
}

tmp<-dtg_final %>% group_by(dprt_time_30min) %>% summarise(n=n())
```

- Cons 5 (Remove)

- Cons 6 (Average assigned time of calling)

```{r}
CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/(A_delta[[i]]^0.5 + A[[i]]^0.5)*60
CallTime[is.nan(CallTime)] <- 999
```

- Cons 7 (Average assigned time of street-hailing)

```{r}
StreetTime <- Rho[[i]]/v[[i]]/(A_delta[[i]] - A[[i]])*log((A_delta[[i]] +1)/(A[[i]]+1))*60
StreetTime[is.nan(StreetTime)] <- 999
```

## Construct GA module

```{r}
library(GA)

f <- function(x){
  cost<- sum(x[1:42])
  return(cost)
}

c1 <- function(x) {
  x<-floor(x)
  conv<-sum(x[1:42])+sum(x[43:47])
  con1 <- max(0,abs(conv)*1000000)
  return(con1)
  }


c2 <- function(x) {
  x<-floor(x)
  con2<-0
  zone_cons <- A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]) + x[1:42]
  #0.65
  
  for (k in 1:42){
    con2 <- con2 + min(0,zone_cons[k])*1000000
  }
  return(con2)
  }

c3 <- function(x){
  x<-floor(x)
  con3<-0
  hub_cons <- B_delta[[i]] + x[43:47]
  for (k in 1:5){
    con3 <- con3 + min(0, hub_cons[k])*1000000
  }
  return(con3)
}

# Average assigned time of calling
c4 <- function(x){
  x<-floor(x)
  con4<-0
  CallTime <- ((pi^0.5*2)/(2^1.5*v[[i]])/((A_delta[[i]]+x[k])^0.5 + A[[i]]^0.5))*60-0.3
  
  
  CallTime[is.nan(CallTime)] <- 999
  for (k in 1:42){
    con4 <- con4 + max(0, CallTime[[k]]*1000000)
  }
  return(con4)
}

#  Average assigned time of street-hailing
c5 <- function(x){
  x<-floor(x)
  con5<-0
  StreetTime <- (Rho/v[[i]]/(A_delta[[i]]+x[k] - A[[i]])*log((A_delta[[i]]+x[k] +1)/(A[[i]]+1)))*60-0.6
  StreetTime[is.nan(StreetTime)] <- 999
  for (k in 1:42){
    con5 <- con5 + max(0, StreetTime*1000000)
  }
  return(con5)
}

zone_min <- -(A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
hub_min <- rep(-sum(zone_min)/4,5)
suggestedSol <- matrix(c(zone_min,hub_min),nrow=1)

ga1 <- ga(
  type = "real-valued",
  fitness = function(x){
    return(-f(x)-c1(x)+c2(x)+c3(x)-c4(x)-c5(x))},
  lower = c(rep(-150,42),rep(0,5)), upper = rep(150,47),
  popSize = 100, maxiter = 100000, run = 2000,
  pmutation = 0.5,
  pcrossover = 0.5,
  suggestions = suggestedSol
)

tmp<-summary(ga1)
solution_x <- floor(tmp$solution[1,])
solution_x
c1(solution_x)
c2(solution_x)
c3(solution_x)
c4(solution_x)
c5(solution_x)
-f(solution_x)
# Efficiency
-f(solution_x)*100/sum(A[[i]]+Psi[[i]])
solution_x + c(A_delta[[i]],B[[i]])

CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/(max(A_delta[[i]]+solution_x[1:42],0)^0.5 + A[[i]]^0.5)*60
StreetTime <- Rho/v[[i]]/(max(A_delta[[i]]+solution_x[1:42],0) - A[[i]])*log((max(A_delta[[i]]+solution_x[1:42],0) +1)/(A[[i]]+1))*60



T<-seq(1,2,0.2)
value<-sapply(1:length(T), function(k){
  # Average assigned time of calling
  c4 <- function(x){
  x<-floor(x)
  con4<-0
  CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/(max(A_delta[[i]]+x[1:42],0)^0.5 + A[[i]]^0.5)*60-T[k]/2
  CallTime[is.nan(CallTime)] <- 999
  for (k in 1:42){
    con4 <- con4 + max(0, CallTime[[k]]*1000000)
  }
  return(con4)
}
  #  Average assigned time of street-hailing
  c5 <- function(x){
    x<-floor(x)
    con5<-0
    StreetTime <- Rho/v[[i]]/(max(A_delta[[i]]+x[1:42],0) - A[[i]])*log((max(A_delta[[i]]+x[1:42],0) +1)/(A[[i]]+1))*60-T[k]
    StreetTime[is.nan(StreetTime)] <- 999
    for (k in 1:42){
      con5 <- con5 + max(0, StreetTime*1000000)
    }
    return(con5)
  }

  zone_min <- -(A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
  hub_min <- rep(-sum(zone_min)/4,5)
  suggestedSol <- matrix(c(zone_min,hub_min),nrow=1)
  
  print(k)

  ga1 <- ga(
    type = "real-valued",
    fitness = function(x){
      return(-f(x)-c1(x)+c2(x)+c3(x)-c4(x)-c5(x))},
    lower = c(rep(-150,42),rep(0,5)), upper = rep(150,47),
    popSize = 100, maxiter = 100000, run = 1000,
    pmutation = 0.1,
    pcrossover = 0.8,
    suggestions = suggestedSol
  )
  
  tmp<-summary(ga1)
  solution_x <- floor(tmp$solution)
  return(-f(solution_x)*100/sum(A[[i]]+Psi[[i]]))
})

plot(T,value*sum(A[[i]]+Psi[[i]]))
value*sum(A[[i]]+Psi[[i]])/100
value2<-value
value2[2]<- -f(solution_x)*100/sum(A[[i]]+Psi[[i]])
plot(T,value2)

```

## Module 2

- Minimize both total assigned time of passengers and operating cost

```{r}
f <- function(x){
  # 7.05$/hour >> 3.5$/30min 
  # or 18626won/hr >> 15.73$/hr >> 7.89$/30min
  CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/((A_delta[[i]]+x[1:42])^0.5 + A[[i]]^0.5)*60
  StreetTime <- Rho/v[[i]]/((A_delta[[i]]+x[1:42]) - A[[i]])*log(((A_delta[[i]]+x[1:42]) +1)/(A[[i]]+1))*60
  CallTime[is.nan(CallTime)]<-999
  StreetTime[is.nan(StreetTime)]<-999
  CallTime[is.infinite(CallTime)]<-999
  StreetTime[is.infinite(StreetTime)]<-999
  PassengerCost <- sum(CallTime*Xi[[i]]+StreetTime*Phi[[i]]) * 7.89
  
  # 6km/liter >> 0.73$/liter >> 8.22km/$ >> 0.12$/km
  # speed: 30km/h >> 15km/30min >> 1.8$/30min
  OperatingCost <- sum(x[1:42])*1.8
  
  TotalCost<-PassengerCost + OperatingCost
  return(TotalCost)
}

# Whole system conservation
c1 <- function(x) {
  conv<-sum(x[1:42])+sum(x[43:47])
  con1 <- max(0,abs(conv)*1000000)
  return(con1)
  }

# Zonal conservation
c2 <- function(x) {
  con2<-0
  zone_cons <- A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]) + x[1:42]
  #0.65
  
  for (k in 1:42){
    con2 <- con2 + min(0,zone_cons[k])*1000000
  }
  return(con2)
  }

# Hub conservation
c3 <- function(x){
  con3<-0
  hub_cons <- B_delta[[i]] + x[43:47]
  for (k in 1:5){
    con3 <- con3 + min(0, hub_cons[k])*1000000
  }
  return(con3)
}

fitness_final<-function(x){
  x2<-floor(x)
  -f(x2)-c1(x2)+c2(x2)+c3(x2)
}

ga2 <- ga(
  type = "real-valued",
  fitness = fitness_final,
  lower = c(rep(-150,42),ifelse(-floor(B_delta[[i]])<0,0,-floor(B_delta[[i]]))),
  upper = rep(150,47) ,
  popSize = 100, maxiter = 100000, run = 2000,
  pmutation = 0.5,
  pcrossover = 0.5
)

tmp<-summary(ga2)
x_solution<-floor(tmp$solution[1,])
x_solution
x_solution+c(A_delta[[i]],B_delta[[i]])

f(x_solution)
f(rep(50,47))
c1(x_solution)
c2(x_solution)
c3(x_solution)
```

## Waiting time of passengers 
- When there is only one vehicle
```{r}
# Call waiting time
(pi^0.5)/(2^1.5*30)*60

# Street waiting time
Rho/30/2*60
```



## Compared to naive relocation

```{r}
## Cost function of Naive relocating
zone_min <- -(A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
hub_min <- rep(-sum(zone_min)/4,5)
suggestedSol <- matrix(c(zone_min,hub_min),nrow=1)
cost_function(suggestedSol)

cost_function <- function(x, waiting_coeffi=9.57, operat_coeffi=1.8){
  # 7.05$/hour >> 3.5$/30min 
  # 22,775won/hr >> 19.14$/hr >> 9.57$/30min
  CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/((A_delta[[i]]+x[1:42])^0.5 + A[[i]]^0.5)*60
  StreetTime <- Rho/v[[i]]/((A_delta[[i]]+x[1:42]) - A[[i]])*log(((A_delta[[i]]+x[1:42]) +1)/(A[[i]]+1))*60
  StreetTime[A_delta[[i]]+x[1:42] == A[[i]]] <- (Rho/v[[i]]/(A[[i]]+1))[A_delta[[i]]+x[1:42] == A[[i]]]
  CallTime[is.nan(CallTime)]<-15
  StreetTime[is.nan(StreetTime)]<-15
  CallTime[is.infinite(CallTime)]<-15
  StreetTime[is.infinite(StreetTime)]<-15
  PassengerCost <- sum(CallTime*Xi[[i]]+StreetTime*Phi[[i]]) * waiting_coeffi
  print(paste0("Passenger cost is ",round(PassengerCost,1), "$"))
  
  # vehicle operating cost: 0.3$/km
  # 6km/l >> 0.73$/liter >> 8.22km/$ >> 0.12$/km
  # speed: 30km/h >> 15km/30min >> 1.8$/30min*veh
  OperatingCost <- sum(A[[i]]+Psi[[i]]+x[1:42])*operat_coeffi
  print(paste0("Operating cost is ",round(OperatingCost,1), "$"))

  
  TotalCost<-PassengerCost + OperatingCost
  print(paste0("Total cost is ",round(TotalCost,1), "$"))
  return(c(PassengerCost,OperatingCost,TotalCost))
}

# Cost function of optimal relocating
cost_function(x_solution)

## Cost function of Naive relocating 
zone_min <- -(A_delta[[i]] - 0.1*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
hub_min <- rep(-sum(zone_min)/4,5)
suggestedSol <- matrix(c(zone_min,hub_min),nrow=1)
cost_function(suggestedSol)
```

## Sensitivity analysis

#### Relocation function
```{r}
relocation_function <- function (uncertain=0.1, waiting_coeffi=9.57, operat_coeffi=1.8, i=1){
  B_delta <- lapply(1:48, function (i) B[[i]] - Eta[[i]] - uncertain * SD_Eta[[i]]) 
  min_y <- sum(ifelse(-floor(B_delta[[i]])>0,-floor(B_delta[[i]]),0))
  min_x <- -(A_delta[[i]] - uncertain*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
  
  f <- function(x){
  # 7.05$/hour >> 3.5$/30min 
  # or 18626won/hr >> 15.73$/hr >> 7.89$/30min
  CallTime <- (pi^0.5*2)/(2^1.5*v[[i]])/((A_delta[[i]]+x[1:42])^0.5 + A[[i]]^0.5)*60
  StreetTime <- Rho/v[[i]]/((A_delta[[i]]+x[1:42]) - A[[i]])*log(((A_delta[[i]]+x[1:42]) +1)/(A[[i]]+1))*60
  StreetTime[A_delta[[i]]+x[1:42] == A[[i]]] <- (Rho/v[[i]]/(A[[i]]+1))[A_delta[[i]]+x[1:42] == A[[i]]]
  CallTime[is.nan(CallTime)]<-15
  StreetTime[is.nan(StreetTime)]<-15
  CallTime[is.infinite(CallTime)]<-15
  StreetTime[is.infinite(StreetTime)]<-15
  PassengerCost <- sum(CallTime*Xi[[i]]+StreetTime*Phi[[i]]) * waiting_coeffi
  
  # 6km/liter >> 0.73$/liter >> 8.22km/$ >> 0.12$/km
  # speed: 30km/h >> 15km/30min >> 1.8$/30min
  OperatingCost <- sum(A[[i]]+Psi[[i]]+x[1:42])*operat_coeffi
  
  TotalCost<-PassengerCost + OperatingCost
  return(TotalCost)
}
  # Whole system conservation
  c1 <- function(x) {
    conv<-sum(x[1:42]) + min_y
    con1 <- max(0,conv)*1000000
    return(con1)
    }
  
  fitness_final<-function(x){
    x2<-floor(x)
    -f(x2)-c1(x2)
  }
  
  ga2 <- ga(
    type = "real-valued",
    fitness = fitness_final,
    lower = min_x,
    upper = rep(150,42) ,
    popSize = 1000, maxiter = 100000, run = 2000,
    pmutation = 0.7,
    pcrossover = 0.2
  )
  
  tmp<-summary(ga2)
  x_solution<-floor(tmp$solution[1,])
  cat("\014")
  return(x_solution)
}

x_tmp<-relocation_function(uncertain=0.1)
cost_function(x_tmp)
sum(x_tmp)
```


#### Uncertainty factor
- Now 0.1
- 0.1 ~ 1 by 0.1
```{r}
i<-1
#Critical point of uncertainty
uncertain<-0.9141
B_delta <- lapply(1:48, function (i) B[[i]] - Eta[[i]] - uncertain * SD_Eta[[i]])
min_y <- sum(ifelse(-floor(B_delta[[i]])>0,-floor(B_delta[[i]]),0))
min_x <- -(A_delta[[i]] - uncertain*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]]))
sum(min_x)+sum(min_y)

uncertain <- seq(0,0.9,0.1)
result_uncertain <- lapply(1:length(uncertain), function(k) relocation_function(uncertain=uncertain[k]))
```

#### Waiting time coefficient
- Now 9.57
- Control 8.6 ~ 10.6 by 1

```{r}
waiting_coeffi <- seq(7.6,11.6,1)
result_waiting <- lapply(1:length(waiting_coeffi), function(k) relocation_function(waiting_coeffi=waiting_coeffi[k]))
```


#### Operating coefficient
- Now 1.8
- Change 0.8 ~ 1.8 by 0.1

```{r}
operat_coeffi <- seq(0.9,1.8,0.1)
result_operat <-lapply(1:length(operat_coeffi), function(k) relocation_function(operat_coeffi=operat_coeffi[k]))
```

#### plot sensitivity

```{r}
library(ggplot2)
tmp<- sapply(result_uncertain,cost_function)
qplot(uncertain,tmp[3,],ylim=c(5500,5800))

tmp2<- sapply(1:length(waiting_coeffi), function(k) cost_function(result_waiting[[k]],waiting_coeffi = waiting_coeffi[[k]]))
plot(waiting_coeffi,tmp2[3,])

tmp3<- sapply(1:length(operat_coeffi), function(k) cost_function(result_operat[[k]],operat_coeffi = operat_coeffi[[k]]))
plot(operat_coeffi,tmp3[3,])

```


## Visualize

```{r}
par(mfrow=c(1,1))
plot(1:48/2,sapply(Xi,sum)+sapply(Phi,sum), ylab="Demand", xlab="Time")
plot(1:48/2,sapply(A,sum)+sapply(Psi,sum), ylab="Supply", xlab="Time")
plot(1:48/2,sapply(A,sum), ylab="Vacant taxis", xlab="Time")
plot(1:48/2,sapply(Psi,sum), ylab="Arrival rate", xlab="Time")
plot(1:48/2,sapply(A_delta,sum), ylab="Supply-Demand", xlab="Time")


minimum_zone <- sapply(1:48, function (i) sum(A_delta[[i]] - 0.68*(SD_Xi[[i]] + SD_Phi[[i]] + SD_Psi[[i]])))
plot(1:48/2,minimum_zone, ylab="Required taxis", xlab="Time")
abline(0,0)
```



```{r}
par(mfrow=c(1,2))
x<-seq(1,100,1)
CallTime <- sapply(1:100, function (k) ((pi^0.5*2)/(2^1.5*v[[i]])/((A_delta[[i]]+x[k])^0.5 + A[[i]]^0.5)*60)[2])
plot(1:100,CallTime)

x<-seq(1,100,1)
StreetTime <- sapply(1:100, function (k) (Rho/v[[i]]/(A_delta[[i]]+x[k] - A[[i]])*log((A_delta[[i]]+x[k] +1)/(A[[i]]+1))*60)[2])
plot(1:100,StreetTime)
```


