 # !diagnostics off

---
title: "AMoD Simulation in R"
author: "Jiho Yeo, Sujin Lee and Jinwoo Lee"
date: '2020 9 29 '
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r}
library(readr)
library(dplyr, warn.conflicts = FALSE)
library(lubridate)
library(sp)
library(GA)
library(amap)
options(dplyr.summarise.inform = FALSE)
```

## Import modules
```{r}
# 위경도/XY직각 좌표계 변환 함수
source('utils/module/CoordChanger.R')

# `passen_final_ROI`을 기반으로 randomly distributed 되게 승하차 좌표와 호출시간을 매핑
source('utils/module/PassengerGenerator.R')

# ZoneIdentifier (Detect zone id from X,y Coordinate)
source('utils/module/ZoneIdentifier.R')

# Make the visualization data for plotly animation
source('utils/module/MakeVisDat')

# Calculate the number of vehicles at all states (idle;assign;oprt;etc)
source('utils/module/TotalNumVeh.R')

# Vehicle Position Updater
source('utils/module/VehiclePositionUpdater.R')

# Model Cost Calculator - calculate the total cost of the model
source('utils/module/ModelCostCalculator.R')

# Convert GA Table to InterReloTable (there is no negative # of relo_vehicles in InterReloTable)
source('utils/module/ConvertTable.R')

# Dispatcher (Dispatch vehicle to passenger)
source('module/Dispatcher.R')
source('module/Dispatcher_intra_relo.R')

#Assign_to_Oprt - Update Vehicle state in assigning(Assign >> Operation)
source('module/Assign_to_Oprt.R')

# Update Vehicle state in operation (Operation >> Idle)
source('module/Oprt_to_Idle.R')

# Relocation Table Calculator
source('module/RelocationTableCalculator.R')
source('module/RelocationTableCalculator_intra.R')

# InterZonalRepositioner (Idle & Relocate >> Assign)
source('module/InterZonalRepositioner.R')
source('module/InterZonalRepositioner_intra.R')

# InterRelo_to_Idle
source('module/InterRelo_to_Idle.R')

# IntraRelo_to_Idle
source('module/IntraRelo_to_Idle.R')


```

## Data preprocessing

#### Import data (Taxi data in Daejeon)

```{r cars}
# Passenger drop on, off data in Daejeon
passen_final<-read_csv("C:/Users/JH/Documents/taxi-relocation/data/passen_final.csv")

# Median travel time between zones
TravelTime<-read_csv("C:/Users/JH/Documents/taxi-relocation/data/TravelTime.csv")

# All passenger pick-up/drop-off in 3 months
### For derive standard deviation of demand
passen_all<-read_csv("C:/Users/JH/Documents/taxi-relocation/data/passen_all.csv")

# Speed over zones by time
speed_by_zone <- read.csv("C:/Users/JH/Documents/taxi-relocation/data/speed_by_zone_time.csv")

# 42 Grids
ROI<-sort(c(61, 105, 136, 146, 154, 168, 184, 189, 190, 191, 194, 196, 199, 206, 225, 229, 230, 231, 233, 240, 241,
       245, 246, 251, 253, 257, 258, 260, 266, 268, 318, 320, 375, 391, 395, 400, 424, 442, 459, 464, 465, 468))

# Grid coordinate
grid<-passen_final %>% select(dprt_grid,dprt_grid_x,dprt_grid_y) %>% filter(dprt_grid %in% ROI) %>% distinct()

# Calculte lower-left and upper-right coordinate of each grid (For detect zone id by x,y coordinate)
grid$X_lower_left<-grid$X_centroid-500
grid$Y_lower_left<-grid$Y_centroid-500
grid$X_upper_right<-grid$X_centroid+500
grid$Y_upper_right<-grid$Y_centroid+500
```

#### Change Coordination

- 위경도 좌표를 직각좌표계로 변환 (격자 Centroid)

```{r}
grid.sp <- SpatialPoints(grid %>% select(-dprt_grid),CRS("+init=epsg:4326")) # 위경도 좌표계 
grid.sp <-  spTransform(grid.sp, CRS("+init=epsg:5181")) # 중부원점 좌표계로 변환
grid_xy <- data.frame(grid.sp)

grid_xy$dprt_grid_x <-  grid_xy$dprt_grid_x  -min(grid_xy$dprt_grid_x )
grid_xy$dprt_grid_y <-  grid_xy$dprt_grid_y  -min(grid_xy$dprt_grid_y )
grid_xy$dprt_grid_x <- trunc(grid_xy$dprt_grid_x/100)*100
grid_xy$dprt_grid_y <- trunc(grid_xy$dprt_grid_y/100)*100

colnames(grid_xy) <- c("X_centroid","Y_centroid")
grid<-cbind(grid,grid_xy)

grid<-grid %>% arrange(X_centroid,Y_centroid)
grid$X_centroid<-grid$X_centroid + 500
grid$Y_centroid<-grid$Y_centroid + 500
grid$id <- 1:nrow(grid)

plot(grid$X,grid$Y)
rm(grid_xy); rm(grid.sp);
```


#### Set pre-determined parameters

```{r}
# Time index; 30 minutes intervals
Time<-ymd_hms("2017-03-02 00:00:00")+hours(0:23)
Time<-c(Time,Time + minutes(30)) %>% sort()

# Length of grid (1km)
L<-1

N<-42 # Number of grids
M<-5
Phi <-vector("list",48) # Call demand density of zones #Phi
Xi <-vector("list",48) # Street demand density of zones #Xi 
k<-0.1 # Ratio between Street and Call demand
Psi<-vector("list",48) # Arrival rate of zones 

Eta<-vector("list",48) # Maximum discharge rate at hubs 

A <- vector("list",48) # Density of vacant vehicles at zones
B <- vector("list",48) # Density of vacant vehicles at stations
v <- vector("list",48) # Vehicle speed
Epsilon <- vector("list",48) # Travel time between zones

# Vehicle Speed
# 일단 15km/h로 고정
VehicleSpeed_km_h<-15
VehicleSpeed <- VehicleSpeed_km_h*1000/60 # meters/min
```

#### Random 한 OD 생성을 위한 historical 승하차 data 가공
```{r}
# Make 30 minutes interval
passen_final$dprt_time_30min <- floor_date(passen_final$dprt_time,"30 minutes")
passen_final$arrvl_time_30min <- floor_date(passen_final$arrvl_time,"30 minutes")

passen_final_ROI <-   passen_final %>% 
  filter(dprt_grid %in% ROI, arrvl_grid %in% ROI) %>%
  arrange(dprt_time_30min)
```

#### `PassengerGenerator`를 통한 Random OD_pairs 생성
```{r}
OD_Pairs_tmp <- PassengerGenerator(passen_final_ROI)
OD_Pairs_tmp$travel_time<-(abs(OD_Pairs_tmp$X_end-OD_Pairs_tmp$X_start)+
                             abs(OD_Pairs_tmp$Y_end-OD_Pairs_tmp$Y_start))/VehicleSpeed # travel_time (min)

OD_Pairs_tmp$arrvl_time<-OD_Pairs_tmp$dprt_time+OD_Pairs_tmp$travel_time*60
OD_Pairs_tmp$arrvl_time_30min <- floor_date(OD_Pairs_tmp$arrvl_time,"30 minutes")
  
# Dataframe을 시간대별 List 형식으로 변경
OD_Pairs <- vector("list",1440)

for(i in 1:1440) {
 OD_Pairs[[i]]<-OD_Pairs_tmp %>% filter(time==i)
}

```

- Naive visualization of demand and supply by time
  - Demand
```{r}
demand<-OD_Pairs_tmp %>% group_by(dprt_time_30min) %>% summarise(demand=n())
plot(demand$dprt_time_30min,demand$demand)
```

  - Supply
```{r}
supply<-passen_final %>% filter(dprt_grid %in% ROI, arrvl_grid %in% ROI) %>% select(carnum, dprt_time_30min) %>%
  group_by(dprt_time_30min) %>% summarise(n=length(unique(carnum)))

plot(supply$dprt_time_30min, supply$n)
```




## Calculate # of Inter-zonal relocated vehicles by using GA - Strategy 1 

- 매 30분마다, 각 존에서 다른 존으로 vehicle을 이동시킴
- 이동시키는 Point는 존 안에 Random point로 보낸 후 나중에 intra-zonal module에서 컨트롤
- 만약 보내야하는 차량의 수가 현재 존의 차량의 수보다 작다면 다음시간대에 나머지 차량들을 보냄

## Set Pre-determined parameters for inter-zonal relocation

#### Define Parameters

```{r}
InterReloTable <- vector("list",1440)
N<-42 # Number of grids
Phi <-vector("list",48) # Call demand density of zones #Phi
Psi<-vector("list",48) # Arrival rate of zones 
A <- vector("list",48) # Density of vacant vehicles at zones
Xi <- 8 # Critical value of the relocation time (min)
Rho<-0.5
C_p <- 15.73 # unit waiting time cost per passenger ($/hr/px) 
C_s <- 1.8 # unit operating time cost per vehicle ($/hr/veh)
C_r <- C_s * 0.5 # operating cost in intra-zonal relocation in Strategy 1 
uncertain <- 0.1 # Uncertainty of the demand and arrival rate 
P_n <- vector("list",48) # Pre-determined number of pods at each zone

```

#### Calculate travel time betweeon zones

```{r}
Tau <- data.frame(grid_start=rep(sort(ROI),each=42),
                  grid_end =sort(ROI))

Tau <- Tau %>% left_join(grid %>% select(grid_start=dprt_grid,
                                         x_start=X_centroid,
                                         y_start=Y_centroid),
                         by="grid_start")

Tau <- Tau %>% left_join(grid %>% select(grid_end=dprt_grid,
                                         x_end=X_centroid,
                                         y_end=Y_centroid),
                         by="grid_end")

Tau$travel_time <- (abs(Tau$x_start-Tau$x_end) + abs(Tau$y_start-Tau$y_end))/VehicleSpeed
head(Tau)
```

#### Calculate passenger demand by zones and time (30-min interval)

```{r}
# Time index; 30 minutes intervals
Time<-ymd_hms("2017-03-02 00:00:00")+hours(0:23)
Time<-c(Time,Time + minutes(30)) %>% sort()

# 42개의 그리드에서 발생한 통행만 추출 > 각 그리드별/시간대별 수요 도출 
tmp<-OD_Pairs_tmp %>% group_by(dprt_grid,dprt_time_30min) %>% summarise(n=n())
tmp2<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
tmp2 <-tmp2 %>% left_join(tmp, by=c("grid_id"="dprt_grid","time"="dprt_time_30min")) %>% arrange(time)
tmp2[is.na(tmp2$n),]$n<-0

for(i in 1:48) {
 Phi[[i]]<-tmp2$n[(N*i-N+1):(N*i)] 
} 

SD_Phi <- lapply(Phi,sqrt)
```

#### Calculate Arrival rate at zones (Psi)

```{r}
tmp <- OD_Pairs_tmp %>% group_by(arrvl_grid,arrvl_time_30min) %>% do(n=length(unique(.$PassengerID)))
tmp$n<-unlist(tmp$n)
tmp <- passen_final %>% filter(trv_dist>0, arrvl_grid %in% ROI) %>% group_by(arrvl_grid,arrvl_time_30min) %>% summarise(n=n())
arate<-data.frame(grid_id=rep(sort(ROI),each=48),time=Time)
arate <-arate %>% left_join(tmp, by=c("grid_id"="arrvl_grid","time"="arrvl_time_30min"))
arate[is.na(arate$n),]$n<-0
arate<-arate %>% arrange(time,grid_id)

for(i in 1:48) {
 Psi[[i]]<-arate$n[(N*i-N+1):(N*i)] 
} 

SD_Psi <- lapply(Psi,sqrt)
```

#### Make random vehicles and distribute them into the region
```{r}
set.seed(43)
InitialVehicle <- data.frame(VehicleID=1:700)
InitialVehicle$X <- runif(nrow(InitialVehicle), min=0, max=7000)
InitialVehicle$Y <- runif(nrow(InitialVehicle), min=0, max=6000)
InitialVehicle$state<-"idle" # state consists of c("idle","assign,"operate","in-relo")
InitialVehicle$time<-1
```

#### Set the number of Idle vehicles at time t and t+1

```{r}
A <- vector("list",48) # Density of vacant vehicles at zones
A_delta <- vector("list",48)
```

#### Define the basis of inter-relocation table

```{r}
RelocationTable <- Tau %>% filter(travel_time <= Xi, travel_time > 0) %>% filter(grid_end>grid_start)
```

#### Derive the adequate number of pods (in Strategy 2 in intra-zonal relocation)

- Zone에 1000m by 1000m 
- Pods이 x개가 있을 때
- X pods들의 X,y 좌표를 계산

```{r}
PodCoord<-vector("list",50)
p <- data.frame(x=rep(0:1000,each=1001), y =0:1000)
PodCoord[[1]] <-data.frame(x=500,y=500)
for (i in 11:50){
  tmp <- Kmeans(p, centers=rbind(PodCoord[[i-1]],
                                 data.frame(x=runif(1,0,1000),y=runif(1,0,1000))),
                method = "manhattan",iter.max=50)
  
  PodCoord[[i]]<- as.data.frame(tmp$center) %>% arrange(x,y)
}

# intra_pod<-function(podnum) {
#   # set.seed(43)
#   p <- data.frame(x=rep(0:1000,each=1001), y =0:1000)
#   tmp <- Kmeans(p, centers=podnum, method = "manhattan",iter.max=50)
#   pod<-as.data.frame(tmp$center) %>% arrange(x,y)
# 
#   return(pod)
# }

```

## Run simulation without Relocation
- Repositioning 알고리즘이 적용되지 않았을 때의 Simulation 구동

```{r}
set.seed(43)

IdleVehicle <- vector("list",1440)
OprtVehicle <- vector("list",1440)
AssignVehicle <- vector("list",1440)
InterReloVehicle <- vector("list",1440)
IntraReloVehicle <- vector("list",1440)

for (i in 1:1439){
  Dispatcher(OD_Pairs, IdleVehicle, time=i)
  Assign_to_Oprt(AssignVehicle,time=i)
  Oprt_to_Idle(OprtVehicle,time=i)
}

# Modify time factor

for (i in 2:1440){
  if (nrow(IdleVehicle[[i]])!=0) IdleVehicle[[i]]$time <- i
  if (nrow(AssignVehicle[[i]])!=0) AssignVehicle[[i]]$time <- i
  if (nrow(OprtVehicle[[i]])!=0) OprtVehicle[[i]]$time <- i
}

TotalNumVeh(1)
TotalNumVeh(2)
TotalNumVeh(3)
TotalNumVeh(4)
```

#### Visualization Vehicles & Passengers 

```{r}
library(viridis)
library(plotly)
library(RColorBrewer)

# Combine idle, assign, oprt vehicles into one dataframe
vis_dat_default <- MakeVisDat(type="no-relo")

tmp <- vis_dat_default %>% filter(time %in% 1:10)

tmp2<-tmp %>% group_by(time) %>% do(data.frame(n_assign=sum(.$state=="assign"),
                                           n_idle=sum(.$state=="idle"),
                                           n_oprt=sum(.$state=="operate"))) %>% filter(time %in% 1:10)

pl <- tmp %>%
  plot_ly(
    x = ~X, 
    y = ~Y, 
    # size = ~pop, 
    # color = ~state, 
    # frame = ~time, 
    text = ~paste('</br> VehicleID: ', VehicleID,
                      '</br> State: ', state), 
    hoverinfo = "text"
  ) %>%
  add_markers(color = ~factor(state),
              # colors = c(viridis(10)[2],viridis(10)[5],viridis(10)[10]),
              frame = ~time) %>%
  # add_text(x = 7500,
  #          y = 1000,
  #          textfont=list(size = 15),
  #          # color=col_assign,
  #          showlegend = FALSE,
  #          text = paste("Assign:",tmp2$n_assign),
  #          frame =tmp2$time) %>%
  layout(xaxis = list(title = "",
                      ticktext = list(0,1,2,3,4,5,6,7), 
                      tickvals = list(0,1000,2000,3000,4000,5000,6000,7000),
                      tickmode = "array",
                      mirror = "ticks",
                      range = c(0, 7000),
                      gridcolor = "grey70",
                      showline = TRUE),
         yaxis = list(title = "",
                      ticktext = list(0,1,2,3,4,5,6), 
                      tickvals = list(0,1000,2000,3000,4000,5000,6000),
                      tickmode = "array",
                      mirror = "ticks",
                      range = c(0, 6000),
                      gridcolor = "grey70",
                      showline = TRUE))%>%
  animation_opts(frame=100,transition = 0, easing = "linear", redraw = FALSE)

pl

xaxis = list(
      ticktext = list("One", "Three", "Five", "Seven", "Nine", "Eleven"), 
      tickvals = list(1, 3, 5, 7, 9, 11),
      tickmode = "array"
  )

tick_layout <- list(
  autotick = FALSE,
  ticks = "outside",
  tick0 = 0,
  dtick = 0.25,
  ticklen = 5,
  tickwidth = 2,
  tickcolor = toRGB("blue")
)

pl
```

#### Save simulation result for visualization

```{r}
save(vis_dat_default, file = "dashboard/vis_dat_default.RData")
#tmp<-CoordChanger(agg_vis_dat %>% select(X,Y))
#agg_vis_dat_WGS <- cbind(agg_vis_dat, tmp)
#agg_vis_dat_WGS<- agg_vis_dat_WGS[-nrow(agg_vis_dat_WGS),]
#write.csv(agg_vis_dat_WGS,"data/vis_dat_default_WGS.csv")
```

- Save the objects with no relocation

```{r}
IdleVehicle_default <- IdleVehicle
AssignVehicle_default <- AssignVehicle
OprtVehicle_default <- OprtVehicle
agg_vis_dat_default <- agg_vis_dat
```


## Run Simulation with only Inter-zonal Relocation

```{r}
set.seed(43)

IdleVehicle <- vector("list",1440)
OprtVehicle <- vector("list",1440)
AssignVehicle <- vector("list",1440)
InterReloVehicle <- vector("list",1440)

InterReloTableGA <- vector("list",48)
InterReloTable <- vector("list",1440)

for (i in 1:1439){
  Dispatcher(OD_Pairs, IdleVehicle, time=i)
  print(paste("Dispacher done at time",i))
  
  Assign_to_Oprt(AssignVehicle,time=i)
  print(paste("Assign to Oprt done at time",i))
  
  Oprt_to_Idle(OprtVehicle,time=i)
  print(paste("Oprt to Idle done at time",i))

  # Calculate Inter-zonal Relocation Table at every 30-min (using GA)
  if((i-1)%%30==0) {
    InterReloTableGA[[(i-1)/30+1]] <- RelocationTableCalculator((i-1)/30+1,max_iter=1, type="inter-relo")
    InterReloTable[[i]]<-rbind(InterReloTable[[i]], ConvertTable(InterReloTableGA[[(i-1)/30+1]]))
    }
  
  InterZonalRepositioner(i)
  print(paste("Update Relocation table and vehicles at time",i))
  
  InterRelo_to_Idle(InterReloVehicle,time=i)
  print(paste("Update Relocate to Idle at time",i))
  
  TotalNumVeh(i)
  print(paste("########## The simulation is done at time",i))
  
}

# Modify time factor

for (i in 2:1440){
  if (nrow(IdleVehicle[[i]])!=0) IdleVehicle[[i]]$time <- i
  if (nrow(AssignVehicle[[i]])!=0) AssignVehicle[[i]]$time <- i
  if (nrow(OprtVehicle[[i]])!=0) OprtVehicle[[i]]$time <- i
  if (!is.null(InterReloVehicle[[i]])) InterReloVehicle[[i]]$time <- i
}

#nrow(IdleVehicle[[10]])+nrow(AssignVehicle[[10]])+nrow(OprtVehicle[[10]])+nrow(InterReloVehicle[[10]])

nrow(IdleVehicle[[1]])+nrow(AssignVehicle[[1]])+nrow(InterReloVehicle[[1]])
TotalNumVeh(1)
TotalNumVeh(2)
TotalNumVeh(3)
TotalNumVeh(4)

TotalNumVeh(500)



#nrow(IdleVehicle[[3]])+nrow(AssignVehicle[[3]])+nrow(OprtVehicle[[3]])+nrow(InterReloVehicle[[3]])
```

#### Visualization Vehicles & Passengers 

```{r}
library(viridis)
library(plotly)
library(RColorBrewer)
MakeVisDat<- function(type="inter-relo"){
  
  agg_IdleVehicle <- do.call(rbind,sapply(1:1440, function (k) IdleVehicle[[k]], simplify = FALSE))
  agg_IdleVehicle <-agg_IdleVehicle %>% select(VehicleID,X,Y,state,time)

  agg_AssignVehicle <- do.call(rbind,sapply(1:1440, function (k) AssignVehicle[[k]], simplify = FALSE))
  agg_AssignVehicle<-agg_AssignVehicle %>% select(VehicleID,X,Y,state,time)

  agg_OprtVehicle <- do.call(rbind,sapply(1:1440, function (k) OprtVehicle[[k]], simplify = FALSE))
  agg_OprtVehicle<-agg_OprtVehicle %>% select(VehicleID,X,Y,state,time)

  
  if (type=="no-relo") {
    # Combine idle, assign, oprt vehicles into one dataframe
    agg_vis_dat <- rbind(agg_IdleVehicle, agg_AssignVehicle, agg_OprtVehicle)
    
    # plotly 시각화를 위해 빈차한대를 임의로 추가
    agg_vis_dat <- rbind(agg_vis_dat, data.frame(VehicleID=999,X=0,Y=0,state="operate",time=1))
    
    return(agg_vis_dat)

  }
    
  if (type=="inter-relo") {
    agg_InterReloVehicle <- do.call(rbind,sapply(1:1440, function (k) InterReloVehicle[[k]], simplify = FALSE))
    agg_InterReloVehicle<-agg_InterReloVehicle %>% select(VehicleID,X,Y,state,time)
    
    # Combine idle, assign, oprt vehicles into one dataframe
    agg_vis_dat <- rbind(agg_IdleVehicle, agg_AssignVehicle, agg_OprtVehicle,agg_InterReloVehicle)
    
    # plotly 시각화를 위해 빈차한대를 임의로 추가
    agg_vis_dat <- rbind(agg_vis_dat, data.frame(VehicleID=999,X=0,Y=0,state="operate",time=1))
    
    return(agg_vis_dat)
  }
    
  if (type=="all-relo") { 
    print("None")
    }
}

vis_dat_inter_relo <- MakeVisDat(type="inter-relo")

tmp <- vis_dat_inter_relo %>% filter(time %in% 1:100)

#1f77b4 or rgb(31, 119, 180)  // muted blue
#ff7f0e or rgb(255, 127, 14)  // safety orange
#2ca02c or rgb(44, 160, 44)   // cooked asparagus green
#d62728 or rgb(214, 39, 40)   // brick red
#9467bd or rgb(148, 103, 189) // muted purple
#8c564b or rgb(140, 86, 75)   // chestnut brown

col_assign<-"#ff7f0e" # safety orange
col_idle<-"#2ca02c" # cooked asparagus green
col_inter<-"#9467bd" # muted purple
col_oprt<- "#d62728" # brick red

col_intra<-"#8c564b" # chestnut brown

pl <- tmp %>%
  plot_ly(
    x = ~X, 
    y = ~Y, 
    # size = ~pop, 
    # color = ~state, 
    # frame = ~time, 
    text = ~paste('</br> VehicleID: ', VehicleID,
                      '</br> State: ', state), 
    hoverinfo = "text"
  ) %>%
  add_markers(color = ~factor(state),
              colors = c("#ff7f0e",viridis(4)[2:4]),
              frame = ~time) %>%
  animation_opts(frame=100,transition = 0, easing = "linear", redraw = FALSE)

pl
```

#### Save simulation result for visualization

```{r}
save(vis_dat_inter_relo, file = "dashboard/vis_dat_inter_relo.RData")
# tmp<-CoordChanger(agg_vis_dat %>% select(X,Y))
# agg_vis_dat_WGS <- cbind(agg_vis_dat, tmp)
# agg_vis_dat_WGS<- agg_vis_dat_WGS[-nrow(agg_vis_dat_WGS),]
# write.csv(agg_vis_dat_WGS,"data/agg_vis_dat_WGS.csv")
```

- Save the objects with only inter-relocation

```{r}
IdleVehicle_inter_relo <- IdleVehicle
AssignVehicle_inter_relo <- AssignVehicle
OprtVehicle_inter_relo <- OprtVehicle
InterReloVehicle_inter_relo <- InterReloVehicle
```


## Run Simulation with Inter- and Intra-zonal Relocation

#### Strategy 1 - equally distributed
```{r}
set.seed(43)

IdleVehicle <- vector("list",1440)
OprtVehicle <- vector("list",1440)
AssignVehicle <- vector("list",1440)
InterReloVehicle <- vector("list",1440)
IntraReloVehicle <- vector("list",1440)

InterReloTableGA <- vector("list",48)
InterReloTable <- vector("list",1440)

for (i in 173:1439){
  Dispatcher_intra_relo(OD_Pairs, IdleVehicle, time=i)
  print(paste("Dispacher done at time",i))
  
  Assign_to_Oprt(AssignVehicle,time=i)
  print(paste("Assign to Oprt done at time",i))
  
  Oprt_to_Idle(OprtVehicle,time=i)
  print(paste("Oprt to Idle done at time",i))
  # TotalNumVeh(i)

  # Calculate Inter-zonal Relocation Table at every 30-min (using GA)
  if((i-1)%%30==0) {
    InterReloTableGA[[(i-1)/30+1]] <- RelocationTableCalculator_intra((i-1)/30+1,max_iter=1, type="intra_s1")
    InterReloTable[[i]]<-rbind(InterReloTable[[i]], ConvertTable(InterReloTableGA[[(i-1)/30+1]]))
    }
  
  InterZonalRepositioner_intra(i)
  print(paste("Update Relocation table and vehicles at time",i))
  # TotalNumVeh(i)
  
  IntraZonalRepositioner(i)
  print(paste("Update Intra-zonal to Idle at time",i))
  # TotalNumVeh(i)
  
  InterRelo_to_Idle(InterReloVehicle,time=i)
  print(paste("Update Inter-Relocate to Idle at time",i))
  # TotalNumVeh(i)
  
  IntraRelo_to_Idle(IntraReloVehicle,time=i)
  print(paste("Update Intra-Relocate to Idle at time",i))
  TotalNumVeh(i)
  print(paste("########## The simulation is done at time",i))
}

TotalNumVeh(3)
TotalNumVeh(4)

# Modify time factor

for (i in 2:1440){
  if (nrow(IdleVehicle[[i]])!=0) IdleVehicle[[i]]$time <- i
  if (nrow(AssignVehicle[[i]])!=0) AssignVehicle[[i]]$time <- i
  if (nrow(OprtVehicle[[i]])!=0) OprtVehicle[[i]]$time <- i
  if (!is.null(InterReloVehicle[[i]])) InterReloVehicle[[i]]$time <- i
}

#nrow(IdleVehicle[[10]])+nrow(AssignVehicle[[10]])+nrow(OprtVehicle[[10]])+nrow(InterReloVehicle[[10]])
TotalNumVeh <- function(time){
  print (paste("Idle is", nrow(IdleVehicle[[time]])))
  print (paste("Assign is", nrow(AssignVehicle[[time]])))
  print (paste("Oprt is", nrow(OprtVehicle[[time]])))
  print (paste("Inter-Relocate is", nrow(InterReloVehicle[[time]])))
  print (paste("Intra-Relocate is", nrow(IntraReloVehicle[[time]])))
  return(nrow(IdleVehicle[[time]])+
           nrow(AssignVehicle[[time]])+
           nrow(OprtVehicle[[time]])+
           nrow(InterReloVehicle[[time]])+
           nrow(IntraReloVehicle[[time]]))
}

nrow(IdleVehicle[[1]])+nrow(AssignVehicle[[1]])+nrow(InterReloVehicle[[1]])
TotalNumVeh(1)
TotalNumVeh(2)
TotalNumVeh(3)
TotalNumVeh(4)

TotalNumVeh(500)



#nrow(IdleVehicle[[3]])+nrow(AssignVehicle[[3]])+nrow(OprtVehicle[[3]])+nrow(InterReloVehicle[[3]])
```

#### Visualization Vehicles & Passengers 

```{r}
library(viridis)
library(plotly)
library(RColorBrewer)


vis_dat_inter_relo <- MakeVisDat(type="inter-relo")

tmp <- vis_dat_inter_relo %>% filter(time %in% 1:100)

pl <- tmp %>%
  plot_ly(
    x = ~X, 
    y = ~Y, 
    # size = ~pop, 
    # color = ~state, 
    # frame = ~time, 
    text = ~paste('</br> VehicleID: ', VehicleID,
                      '</br> State: ', state), 
    hoverinfo = "text"
  ) %>%
  add_markers(color = ~factor(state),
              colors = viridis(4),
              frame = ~time) %>%
  animation_opts(frame=100,transition = 0, easing = "linear", redraw = FALSE)

pl
```

#### Save simulation result for visualization

```{r}
save(vis_dat_inter_relo, file = "dashboard/vis_dat_inter_relo.RData")
# tmp<-CoordChanger(agg_vis_dat %>% select(X,Y))
# agg_vis_dat_WGS <- cbind(agg_vis_dat, tmp)
# agg_vis_dat_WGS<- agg_vis_dat_WGS[-nrow(agg_vis_dat_WGS),]
# write.csv(agg_vis_dat_WGS,"data/agg_vis_dat_WGS.csv")
```

- Save the objects with only inter-relocation

```{r}
IdleVehicle_inter_relo <- IdleVehicle
AssignVehicle_inter_relo <- AssignVehicle
OprtVehicle_inter_relo <- OprtVehicle
InterReloVehicle_inter_relo <- InterReloVehicle
```

## Cost Calculator in Simulation
- 시뮬레이션이 작동함에 따라 total cost가 계산되도록 하는 모듈

#### Assigned & waiting time cost

```{r}
CalculateAssignCost <- function(AssignVehicle){
  tmp<-do.call(rbind,sapply(1:1440, function (k) AssignVehicle[[k]], simplify = FALSE))
  # tmp2<-tmp %>% group_by(X_start,Y_start) %>% 
  #   do(data.frame(start_x=.$X[1],start_y=.$Y[1],end_x=.$X_start[nrow(.)],end_y=.$Y_start[nrow(.)]))
  # tmp2$travel_dist <- abs(tmp2$start_x-tmp2$end_x) + abs(tmp2$start_y-tmp2$end_y)
  
  # 분단위로 cost 계산 (1분에 차량속도만큼 움직였다고 가정)
  tmp2 <- data.frame(table(tmp$time))
  colnames(tmp2) <- c("time","total_assign_time")
  tmp2$time<-as.numeric(tmp2$time)/60
  
  # 30분 단위로 표출
  tmp2$time_30min <- trunc((as.numeric(tmp2$time)/30))
  tmp3 <- tmp2 %>% group_by(time_30min) %>% summarise(total_assign_time=sum(total_assign_time))
  return(tmp3)
}

AssignCost_default<-CalculateAssignCost(AssignVehicle_default)
qplot(AssignCost_default$time_30min,AssignCost_default$total_assign_time,geom="line")+ylim(0,250)+xlim(0,24)

AssignCost_inter_relo<-CalculateAssignCost(AssignVehicle_inter_relo)
qplot(time_30min,total_assign_time,data=AssignCost_inter_relo,geom="line")+ylim(0,250)+xlim(0,24)
```

#### Relocation cost

```{r}
CalculateInterRelocationCost <- function(InterReloVehicle){
  tmp<-do.call(rbind,sapply(1:1440, function (k) InterReloVehicle[[k]], simplify = FALSE))
  # tmp2<-tmp %>% group_by(X_start,Y_start) %>% 
  #   do(data.frame(start_x=.$X[1],start_y=.$Y[1],end_x=.$X_start[nrow(.)],end_y=.$Y_start[nrow(.)]))
  # tmp2$travel_dist <- abs(tmp2$start_x-tmp2$end_x) + abs(tmp2$start_y-tmp2$end_y)
  
  # 분단위로 cost 계산 (1분에 차량속도만큼 움직였다고 가정)
  tmp2 <- data.frame(table(tmp$time))
  colnames(tmp2) <- c("time","total_relocated_time")
  tmp2$time<-as.numeric(tmp2$time)/60
  
  # 30분 단위로 표출
  tmp2$time_30min <- trunc((as.numeric(tmp2$time)/30))
  tmp3 <- tmp2 %>% group_by(time_30min) %>% summarise(total_assign_time=sum(total_assign_time))
  return(tmp3)
}

AssignCost_default<-CalculateAssignCost(AssignVehicle_default)
qplot(AssignCost_default$time_30min,AssignCost_default$total_assign_time,geom="line")+ylim(0,250)+xlim(0,24)

AssignCost_inter_relo<-CalculateAssignCost(AssignVehicle_inter_relo)
qplot(time_30min,total_assign_time,data=AssignCost_inter_relo,geom="line")+ylim(0,250)+xlim(0,24)


CalculateIntraRelocationCost <- function(){
  
  
}

```


## Calculate the cost of the model
- Cost function

```{r}
ModelCostCalculator(InterReloTableGA[[1]]$num_relo)
```
